---
title: "Workbook"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1: Motivation

### Problem Statement
- High Costs per click with SEM (Search Engine Marketing)
- Airline industry a Competitive market with Low margins

### State the Questions
- Where do we allocate our marketing budget most efficiently?
- How can we reduce Cost/Click, increase revenue and optimize performance?
- Do branded keywords bring in more revenue?
- What is the single-click conversion rate of branded / unbranded keywords?
- Are broad or focused keywords more profitable?
- Can assist keywords help increase conversion rate?
- Which search engine delivers the most ROI
- customer segments / search engine
  --> Specific pattern in buying behavior?

### Main Objectives
- Minimize Cost/Click
- Maximize Revenue
- Maximize Single-click conversion
- Maximize Profitability
- Maximize Conversion Rate

## What could be a positive outcome?

# Part 2: Method

## What key resources do we acquire?

Data:
- Description
- Type: xls

Libraries:
```{r}
library(readxl)
```

## What is our approach to solve the problem?

### Inspect & Import data
R tries to import the first sheet of the excel file which resolves in an error. This is why the argument read_excel function has to be used to specifiy the column.

```{r}

# Inspect sheets of excel-file
excel_sheets('C:/Users/LK/Nextcloud7/Personal/Docs/case-studies/Air France/assets/Air France Case Spreadsheet Supplement.xls')
```

```{r}
# Import data
kayak <- read_excel("C:/Users/LK/Nextcloud7/Personal/Docs/case-studies/Air France/assets/Air France Case Spreadsheet Supplement.xls", 
                                                     sheet = "Kayak")

doubleclick <- read_excel("C:/Users/LK/Nextcloud7/Personal/Docs/case-studies/Air France/assets/Air France Case Spreadsheet Supplement.xls", 
                         sheet = "DoubleClick")

```


Are all the imported variables important?
Useful variables in the dataset

$campaigns
$impressions
$click-through
$Cost/Click
$Revenue 
$Single-click conversion
$Profitability
$Conversion Rate

### Explore Data

##Massaging

##Descriptive

Plots
Statistics
Correlation
Association

## Predictive

Feature Selection
Apply ML-Algorithmus

# Mechanics

Distribution

Stats

Boxplot

Outlier

# Message

Key Findings

The C-suite of ___ face the following (problem/challenge), which is best solved with _ (solution) having an impact and/or making profits via ___ . The unique advantages/differentiators of the MVP are ____ , when comparing with the following key competitors / alternatives: ___

Next steps

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
