---
title: "Untitled"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Import Libraries
library(readxl)
library(tidyr)
library(plotly)
library(dplyr)

# Import data
kayak <- read_excel("Spreadsheet_Data.xls", 
                                                     sheet = "Kayak")

doubleclick <- read_excel("Spreadsheet_Data.xls", 
                         sheet = "DoubleClick")

#Convert to dataframe
doubleclick <- as.data.frame(doubleclick)

#Look for weird stuff
table(doubleclick$`Match Type`)

# The NAs have to be removed.
doubleclick_clean <- na.omit(doubleclick)

# Notice how the number of rows gets reduced 
print(nrow(doubleclick_clean))

# Look for Spelling mistakes
unique(doubleclick_clean $`Bid Strategy`)

# Replace Typos
doubleclick_clean$`Bid Strategy` <- gsub("Postiion 1-4 Bid Strategy","Position 1-4 Bid Strategy",doubleclick_clean$`Bid Strategy`)

doubleclick_clean$`Bid Strategy` <- gsub("Position 1 -2 Target","Position 1-2 Target",doubleclick_clean$`Bid Strategy`)


# Create data set for analysis
sem <- doubleclick_clean[,c('Campaign','Keyword','Keyword Group','Publisher Name', 'Bid Strategy','Engine Click Thru %','Match Type','Trans. Conv. %','Total Cost/ Trans.','Impressions')]

clickthrough_publisher <- aggregate(sem$`Engine Click Thru %`, by=list(sem$`Publisher Name`), FUN=mean) 
```



```{r clickthrough, echo = FALSE, message=FALSE, warning=FALSE}
# Clickthrough rate
plot_ly(clickthrough_publisher, x = clickthrough_publisher$`Group.1`, y=~`x`,title = 'Average Clickthrough rate of different publisher')%>%
        layout(title = 'Clickthrough per Publisher', plot_bgcolor = "#e5ecf6",xaxis = list(title = 'Publisher'),yaxis = list(title = 'Clickthrough Rate in %'))
```

### Slide with Plot

```{r pressure}

```
### Motivation
- High Costs per click with SEM (Search Engine Marketing)
- Airline industry a Competitive market with Low margins


```{r hhh, echo = FALSE, message=FALSE, warning=FALSE}

```
### Target Goals
- Where do we allocate our marketing budget most efficiently?
- How can we reduce Cost/Click, increase revenue and optimize performance? 
- Which search engine delivers the most ROI?
- what are the customer segments / search engine

```{r}

```

### Data Description 

-Campaigns
-Impressions
-Click-through
-Cost/Click
-Revenue 
-Single-click conversion
-Profitability
-Conversion Rate

```{r}

```

### Key Findings

-


### Recommendations for the future

- Do branded keywords bring in more revenue?
- Are broad or focused keywords more profitable?
- Can assist keywords help increase conversion rate?


