---
title: "Air France | Team 13"
output:
  slidy_presentation: default
  beamer_presentation: default
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Import Libraries
library(readxl)
library(tidyr)
library(plotly)
library(dplyr)

# Import data
kayak <- read_excel("Spreadsheet_Data.xls", 
                                                     sheet = "Kayak")

doubleclick <- read_excel("Spreadsheet_Data.xls", 
                         sheet = "DoubleClick")
#Convert to dataframe
doubleclick_clean <- as.data.frame(doubleclick)

#Look for weird stuff
colSums(is.na(doubleclick_clean))
table(doubleclick_clean$`Bid Strategy`)

# Replace NA entries  in bid strategy with Unassigned
doubleclick_clean$`Bid Strategy`[is.na(doubleclick_clean$`Bid Strategy`)] = "Unassigned"

# Notice how the number of rows gets reduced 
print(nrow(doubleclick_clean))

# Look for Spelling mistakes
unique(doubleclick_clean $`Bid Strategy`)

# Replace Typos
doubleclick_clean$`Bid Strategy` <- gsub("Postiion 1-4 Bid Strategy","Position 1-4 Bid Strategy",doubleclick_clean$`Bid Strategy`)

doubleclick_clean$`Bid Strategy` <- gsub("Position 1 -2 Target","Position 1-2 Target",doubleclick_clean$`Bid Strategy`)

# Create data set for analysis
sem <- doubleclick_clean[,c('Campaign','Keyword','Keyword Group','Publisher Name', 'Bid Strategy','Engine Click Thru %','Match Type','Trans. Conv. %','Total Cost/ Trans.','Impressions','Total Volume of Bookings')]

# Average out the clickthroughs per publisher
clickthrough_publisher <- aggregate(sem$`Engine Click Thru %`, by=list(sem$`Publisher Name`), FUN=mean) 

# Sum up Transactions per publisher
transactions_publisher <- aggregate(sem$`Total Volume of Bookings`, by=list(sem$`Publisher Name`), FUN=sum) 

# Average out the costs per transaction per publisher
costs_publisher <- aggregate(sem$`Total Cost/ Trans.`, by=list(sem$`Publisher Name`), FUN=mean) 

# Average out the costs per transaction per Strategy
costs_strategy <- aggregate(sem$`Total Cost/ Trans.`, by=list(sem$`Bid Strategy`), FUN=mean) 
```


## Problem Statement
- High Costs per click with SEM (Search Engine Marketing)
- Airline industry a Competitive market with Low margins

***

## Target Goals
- Where do we allocate our marketing budget most efficiently?
- How can we reduce Cost/Click, increase revenue and optimize performance?
- Which search engine delivers the most ROI?

***

## Variables of Interest 
- Campaigns
- Impressions
- Click-through
- Cost/Click
- Revenue 
- Single-click conversion
- Conversion Rate

## Method

- Get familiar with case
- State Key Problems
- Import Data
- Massage Data | Rename NAs
- Descriptive
- Aggregate, Analyze and Visualize
- Summarize Key Findings


## Key Findings | Performance Publisher

```{r clickthrough, echo = FALSE, message=FALSE, warning=FALSE}
# Clickthrough rate
plot_ly(clickthrough_publisher, x = clickthrough_publisher$`Group.1`, y=~`x`,title = 'Average Clickthrough rate of different publisher')%>%
        layout(title = 'Clickthrough per Publisher', plot_bgcolor = "#e5ecf6",xaxis = list(title = 'Publisher'),yaxis = list(title = 'Clickthrough Rate in %'))
```

## Key Findings | Bookings per Publisher

```{r bookings, echo = FALSE, message=FALSE, warning=FALSE}
# Visualize transactions per publisher
plot_ly(transactions_publisher, x = transactions_publisher$`Group.1`, y=~`x`,title = 'Bookings per publisher')%>%
        layout(title = 'Bookings per publisher', plot_bgcolor = "#e5ecf6",xaxis = list(title = 'Publisher'),yaxis = list(title = 'Transactions'))
```

## Key Findings | Transaction Costs per Publisher

```{r transactions, echo = FALSE, message=FALSE, warning=FALSE}
# Visualize average costs per transaction per engine
plot_ly(costs_publisher, x = costs_publisher$`Group.1`, y=~`x`)%>%
        layout(title = 'Average Costs per Publisher', plot_bgcolor = "#e5ecf6",xaxis = list(title = 'Publisher'),yaxis = list(title = 'Costs / Transaction'))
```

## Key Findings | Transaction Costs per Strategy

```{r costs, echo = FALSE, message=FALSE, warning=FALSE}
# Visualize average costs per transaction per engine
plot_ly(costs_strategy, x = costs_strategy$`Group.1`, y=~`x`)%>%
        layout(title = 'Average Costs per Strategy', plot_bgcolor = "#e5ecf6",xaxis = list(title = 'Publisher'),yaxis = list(title = 'Costs / Transaction'))
```

## Next Steps

- Do branded keywords bring in more revenue?
- Are broad or focused keywords more profitable?
- Can assist keywords help increase conversion rate?

