---
title: "Untitled"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Import Libraries
library(readxl)
library(tidyr)
library(plotly)
library(dplyr)

# Import data
kayak <- read_excel("Spreadsheet_Data.xls", 
                                                     sheet = "Kayak")

doubleclick <- read_excel("Spreadsheet_Data.xls", 
                         sheet = "DoubleClick")
#Convert to dataframe
doubleclick_clean <- as.data.frame(doubleclick)

#Look for weird stuff
colSums(is.na(doubleclick_clean))
table(doubleclick_clean$`Bid Strategy`)

# Replace NA entries  in bid strategy with Unassigned
doubleclick_clean$`Bid Strategy`[is.na(doubleclick_clean$`Bid Strategy`)] = "Unassigned"

# Notice how the number of rows gets reduced 
print(nrow(doubleclick_clean))

# Look for Spelling mistakes
unique(doubleclick_clean $`Bid Strategy`)

# Replace Typos
doubleclick_clean$`Bid Strategy` <- gsub("Postiion 1-4 Bid Strategy","Position 1-4 Bid Strategy",doubleclick_clean$`Bid Strategy`)

doubleclick_clean$`Bid Strategy` <- gsub("Position 1 -2 Target","Position 1-2 Target",doubleclick_clean$`Bid Strategy`)

```

## Problem Statement
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

## Analysis | Performance Publisher

```{r clickthrough, echo = FALSE, message=FALSE, warning=FALSE}
# Clickthrough rate
plot_ly(clickthrough_publisher, x = clickthrough_publisher$`Group.1`, y=~`x`,title = 'Average Clickthrough rate of different publisher')%>%
        layout(title = 'Clickthrough per Publisher', plot_bgcolor = "#e5ecf6",xaxis = list(title = 'Publisher'),yaxis = list(title = 'Clickthrough Rate in %'))
```

## Slide with Plot

```{r pressure}

plot(pressure)
```

## # Part 1: Motivation

### Problem Statement
- High Costs per click with SEM (Search Engine Marketing)
- Airline industry a Competitive market with Low margins


```{r hhh, echo = FALSE, message=FALSE, warning=FALSE}

```

