---
title: "Documentation_Marketing-Campaign"
author: "Timon-Laurin Krämer"
date: "11/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Motivation

## Method

## Mechanics

1. Importing

```{r}
# Import libraries
library(readxl)
library(BBmisc)

# Import data
mark_cmp <- read_excel("datasets_marketing_campaign_SF.xlsx")

# Inspect
colSums(is.na(mark_cmp))

# Convert 
mark_cmp <- as.data.frame(mark_cmp)

```
2. Massaging

```{r}
library(tidyr)

# Remove NAs
mark_cmp <- drop_na(mark_cmp)

# Create dummy variables
library('fastDummies')
dummy <- dummy_cols(mark_cmp, select_columns = c('Education', 'Marital_Status','Country'))

# Change date variable from character to date
mark_cmp$Dt_Customer <- as.Date(mark_cmp$Dt_Customer)

# Write csv
write.csv(mark_cmp,"C:/Users/LK/Nextcloud7/Personal/Docs/case-studies/Marketing Campaign/data.csv", row.names = FALSE)


```

3. Descriptive

4. Predictive

### Motivation
Use of linear regression to classify the important variables that help us predict web purchases. 

### Method
- Checklist for Regression
- Split into training and test data
- Scale data

### Mechanics

```{r}

# Scale the data
scaled_mark = normalize(mark_cmp, method = "range", range = c(0, 1))

# Split into training and test
train_index <- sample(1:nrow(mark_cmp),size=0.8*nrow(mark_cmp))
mark_train <- mark_cmp[train_index,]
mark_test <- mark_cmp[-train_index,]

# Train the model
model <- lm(NumWebPurchases ~ ., data=mark_train)
summary(model)

# Get residuals
res <- resid(model)

# Produce residual vs. fitted plot
plot(fitted(model), res)
qqnorm(res)


pred <- predict(model,mark_test)


# Test the model
plot(pred,mark_test$NumWebPurchases)

```
We concluded that a few variables are not statistically significant. Therefore, we trained the model again using only the relevant variables. 

```{r}
better_model <- lm(NumWebPurchases ~ Income + Kidhome + Teenhome + MntWines + MntSweetProducts + MntGoldProds + NumDealsPurchases +NumStorePurchases +NumWebVisitsMonth, data=mark_train)
summary(model)


```
### Message 

Interpret Business Success -> Odds

### Motivation

- Do US-Customers buy more than the rest of the world?

### Method

- Aggregate columns to get the number of total purchases
- Split into US and Rest of the world

## Mechanics

```{r}

# Aggregate total purchases
mark_cmp$Total_Purch <- mark_cmp$NumDealsPurchases + mark_cmp$NumWebPurchases + mark_cmp$NumCatalogPurchases + mark_cmp$NumStorePurchases

table(mark_cmp$Country)

mark_cmp[which(mark_cmp)]


sdoihsodihoishd

```






